\textls[-0]{\thetitle}

### 2023-03-14 canonicitymodel.tex
Add details about Grothendieck Universe

Like most logical relation proof,  we interpret each judgement, inductively interpret each syntax piece. We are working on an intrinsic setting thus even we omit context for brevity, the syntax piece is still well-typed. We will omit the treatment of the universe and the verification of most equality for simplicity (and the treatment of the universe will not affect our model). Interested audience can refer to \citet{kaposi2019gluing, coquand2018canonicity,sterling2019algebraic} for a complete technical treatements.

>>>>

We first need the mathmatical setup to interpret universe level, following \citet{sterling2019algebraic}:

\newcommand{\Set}[1]{\ensuremath{\texttt{Set}_{#1}}}

{\textbf{Set-theoretic Universe Assumption.}} As a simplifying move, we assume an infinite hierarchy of Grothendieck universes $\Set{i}$ for $i \in \mathbb{N}$ in our meta-logic.

For people familiar with Agda, we can roughly consider Grothendieck Universe $\Set{i}$ as the $\Set{i}$ in Agda. In other words, each $\Set{i}$ is 
\begin{itemize}
  \item Closed under dependent function type and dependent tuple type. For example, when we have $\denotesC{A}, \denotes{B} \in \Set{i}$, we will have $\denotes{\TyPi{A}{B}} \in \Set{i}$
  \item the hierarchy is cumulative as $\Set{i} \in \Set{i+1}$ and $\Set{i} \subseteq \Set{i+1}$
\end{itemize}

Like most logical relation proof,  we interpret each judgement and inductively interpret each syntax piece. We are working on an intrinsic setting thus even if we omit context for brevity, the syntax piece is still well-typed. 
% We will omit the treatment of the universe and the verification of most equality for simplicity (and the treatment of the universe will not affect our model). Interested audience can refer to \citet{kaposi2019gluing, coquand2018canonicity,sterling2019algebraic} for a complete technical treatements.
